Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-12 paper/disc20clustering.tex
The right insigths into generalizing LB

First, we construct a ground set of size $k-1$ on an arbitrarily chosen cluster.
In any partition, there must exist an isolated node collocated with the ground set of size $k-1$, and we call it \emph{special}.
We issue requests between the current special node, and some node that was initially collocated with it.
Repeating such requests, almost all the nodes must visit the cluster $S$.
In comparison, we show that there exists an optimal offline algorithm \OPT that performs only two migrations.
Figure~\ref{fig:lb} illustrates the constructs used in the lower bound.

@@

\begin{proof}
	Fix any online algorithm \ALG{}.
	Let $I(C)$ denote the cluster where nodes of the ground set $C$ are located in the initial partition.
	If $C$ contains nodes that originate from different clusters, $I(C)$ is undefined.
	Throughout the construction, we maintain ground sets for each node.
	Initially, all nodes are isolated (i.e., in ground sets of size $1$).
	First, we create a ground set $B$ of $k-1$ nodes on an arbitrarily chosen cluster (the nodes  are already collocated).
	%We never dismiss any constructed ground set.
	Each cluster hosts exactly $k$ nodes, and in any partition, a single isolated node resides in $S$.
	We say that this isolated node that accompanies the ground set $B$ is \emph{special}.
	We denote the first special node by $x_0$.

	Then, we add the special node to a larger ground set to force its eviction.
	Precisely,
	we create a ground set $\{x_0, y_0\}$, 
	where $x_0$ is the current special node and $y_0$ is an arbitrary node that does not reside in $S$.
	\ALG has them split, and the adversary issues external requests until \ALG collocates them.
	There is no space to accommodate $\{x_0, y_0\}$ in the cluster of $x_0$ (as $B$'s size is $k-1$), hence \ALG must collocate $\{x_0, y_0\}$ in another cluster.
	To preserve a feasible partition of nodes into clusters after collocating $\{x_0, y_0\}$,
	\ALG must replace $x_0$ with another single node that we call $x_1$.

@@

\noindent
\textbf{Lower bound for the general problem.}
For a lower bound $\Omega(k\cdot \ell)$ for the general partitioning problem, the adversary continues to issue requests to split nodes of a ground set until the algorithm collocates them.
The ground sets constructed in our lower bound can be perfectly partitioned into the clusters.
This way, the optimal algorithm moves to a perfect partition at the beginning (where requests incur the cost~$0$), thus its cost is bounded.
If the algorithm splits any pair of nodes of a ground set, the adversary issues requests to any pair of split nodes.
These two observations imply that the algorithm must eventually collocate all nodes of a~ground set to be competitive.
The construction is oblivious to the choice of the reconfiguration cost $\alpha$: we compare the 	number of node exchanges of \ALG and \OPT.

>>>>

We start by constructing a ground set of size $k-1$ on an arbitrarily chosen cluster.
In any partition, there must exist an isolated node collocated with the ground set of size $k-1$, and we call it \emph{special}.
We issue requests between the current special node, and some node that was initially collocated with it.
Repeating such requests, almost all the nodes must visit the cluster $S$.
In comparison, we show that there exists an optimal offline algorithm \OPT that performs only two migrations.
Figure~\ref{fig:lb} illustrates the constructs used in the lower bound.

@@

\begin{proof}
	Fix any online algorithm \ALG{}.
	Let $I(C)$ denote the cluster where nodes of the ground set $C$ are located in the initial partition.
	If $C$ contains nodes that originate from different clusters, $I(C)$ is undefined.
	Throughout the construction, we maintain ground sets for each node.
	Initially, all nodes are isolated (i.e., in singleton ground sets).
	First, we create a ground set $B$ of $k-1$ nodes on an arbitrarily chosen cluster (the nodes  are already collocated).
	%We never dismiss any constructed ground set.
	Each cluster hosts exactly $k$ nodes, and in any partition, a single isolated node resides in $S$.
	We say that this isolated node that accompanies the ground set $B$ is \emph{special}.
	We denote the first special node by $x_0$.

	Then, we add the special node to a larger ground set to force its eviction.
	Precisely,
	we create a ground set $\{x_0, y_0\}$, 
	where $x_0$ is the current special node and $y_0$ is an arbitrary node that does not reside in $S$.
	\ALG has them split, and the adversary issues external requests until \ALG collocates them.
	There is no space to accommodate $\{x_0, y_0\}$ in the cluster of $x_0$ (as $B$'s size is $k-1$), hence \ALG must collocate $\{x_0, y_0\}$ in another cluster.
	To preserve a~feasible partition of nodes into clusters after collocating $\{x_0, y_0\}$,
	\ALG must replace $x_0$ with another single node that we call $x_1$.

@@

\noindent
\textbf{Lower bound for the general problem.}
For a lower bound $\Omega(k\cdot \ell)$ for the general partitioning problem, the adversary continues to issue requests to split nodes of a ground set until the algorithm collocates them.
Note that the ground sets constructed in our lower bound can be perfectly partitioned into the clusters.
Hence, the optimal algorithm moves to a perfect partition at the beginning (where requests incur the cost~$0$), and its cost is bounded.
This means that the algorithm must eventually collocate all nodes of a~ground set to be competitive.
We reveal the next ground set only after the collocation, hence we can repeat the analysis of the algorithm for the learing problem.
Finally, we note that the construction is oblivious to the choice of the reconfiguration cost $\alpha$: we compare the 	number of node exchanges of \ALG and \OPT.
